Strong Gravitational Lensing Finding Challenge

### 2017-03-02 paper.tex
Edit.

\begin{figure}
 \includegraphics[width=\columnwidth]{Cabanac/arcmethod.pdf}
 \caption{\footnotesize  GAHEC IRAP) From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties. 
}
 \label{fig:Cabanac}
\end{figure}

@@

\red{Referenc to figure \ref{fig:Cabanac}?}
\section{results}

@@

>>>>

\begin{figure}
 \includegraphics[width=\columnwidth]{Cabanac/arcmethod.pdf}
 \caption{ (GAHEC IRAP) From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties. }
 \label{fig:Cabanac}
\end{figure}

@@

\red{Reference to figure \ref{fig:Cabanac}?}
\section{results}

@@

Human inspection was the only method to find the jackpot lens
